### 2017-06-27 Elle/Elle.tex
Elle modified

\noindent
Should not be able to derive exchange in Elle comonadicly or monadicly.:

>>>>

\noindent
Deriving exchange in Elle comonadicly:

\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
    \inferrule* [right={\tiny tenL}] {
      $$\mprset{flushleft}
    \inferrule* [right={\tiny Fl}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny beta}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny tenR}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny ax}] {
                \,
              }{[[y0 : Gf B |- y0 : Gf B]]}
            }{[[y0 : Gf B; . |- F y0 : F Gf B]]}
            \\
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny ax}] {
                \,
              }{[[x0 : Gf A |- x0 : Gf A]]}
            }{[[x0 : Gf A; . |- F x0 : F Gf A]]}
          }{[[y0 : Gf B, x0 : Gf A ; . |- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A]]}
        }{[[x1 : Gf A, y1 : Gf B ; . |- ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0) : h(F Gf B) (x) F Gf A]]}
      }{[[x1 : Gf A ; y2 : F Gf B |- let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)) : h(F Gf B) (x) F Gf A]]}
    }{[[. ; x2 : F Gf A, y2 : F Gf B |- let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0))) : h(F Gf B) (x) F Gf A]]}
    }{[[. ; z : h(F Gf A) (x) F Gf B |- let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf B) (x) F Gf A)]]}
    }{[[. ; . |- \l z : h(F Gf A) (x) F Gf B . let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf A) (x) F Gf B) -> (h(F Gf B) (x) F Gf A)]]}
  \end{math}
\end{center}
